Macro Impacts

### 2016-08-04 Macro Impacts Revised.tex
Figured out how to make it work!
In a discussion with Josh, we bring up some issues with my method, and
I propose a resolution at the end of page 24.

\f{E_m'}{N}=\f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{P_m(\vec k)}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}

@@

The approximation (32) holds when $lk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus

@@

\f{E_m'}{N} &= \f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\

@@

&\times (b^2f_1(b)-a^2f_1(a))^2\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2p_0(m)^2\,,\\

@@

&\times \underbrace{\f{(b^2f_1(b)-a^2f_1(a))^2}{\int r\diff r f(r)^2}}_{A}F_{m,n}^2 2\rho_m\sigma_Xv_X^2\,.

@@

E_m' =  4 l  \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} F_{m,n}^2 A2\rho_m\sigma_Xv_X^2\,.

@@

>>>>

\f{E_m'}{N}=\f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}\int\f{\diff^3 k}{(2\pi)^3}\abs{P_m(\vec k)}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}

@@

Because $Q_{m,n}$ and $T_{m,n}$ take into account the material properties along the path of the ray, the coefficients out front, which are those of the origin of the ray, act as a normalization, so that in the case of no refraction/reflection and anelastic attenuation the energy is that of the ray at the start of its journey.
The approximation (32) holds when $bk_0\ll 2$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus

@@

\f{E_m'}{N} &= \f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\

@@

&\times (b^2f_1(b)-a^2f_1(a))^2\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}p_0(m)^2\,,\\

@@

&\times \underbrace{\f{(b^2f_1(b)-a^2f_1(a))^2}{\int r\diff r f(r)^2}}_{A}F_{m,n} 2\rho_m\sigma_Xv_X^2\,.

@@

E_m' =  4 l  \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} F_{m,n} A2\rho_m\sigma_Xv_X^2\,.

@@

POSSIBLE REASONING: This computation is justified in itself, since $b$, even after non-linear evolution, is at most on the order of 10s to 100s of meters - and based on the size of the plastic zone potentially millimeters, $k_0 = 12\te{km}^{-1}$ times $b$ is at most $10^{-1}\ll 2$ so the leading order term in the Hypergeometric series dominates.
AHA! $k_0$ should be the LOWER frequency i.e. $0.012\te{km}^{-1}$, since any lower would mean it is undetectable, but any higher and we could be over-estimating the amount of attenuation!!!! HAHA!
\section{New Calculation}
Instead of the hypergeometric function, whose form is unnecessarily linked to the profile of the pressure wave, suppose the pressure wave has the Fourier transform
\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}F(b k\sin\theta)
and write
F^2 = \sum_{i = 0}^\infty G_i \times (bk\sin\theta)^i\,.
The term $e^{-k\f{Q}{T}}$ tells us at what point we can stop the integral.
